\documentclass{friggeri-cv}
\begin{document}
\header{matt}{sicker}{functional software craftsman}

% sidebar
\begin{aside}
    \section{about}
    \phone{847-736-8133}
    \email{mattsicker@apache.org}
    \website{musigma.blog}
    \website{github.com/jvz}
    \section{programming}
    Scala, Kotlin, Java
    Bash, Python, Groovy
    Ruby, Lisp, C, C++
    SQL, Haskell, \LaTeX
    HTML, CSS, JavaScript
    PHP
    \section{frameworks}
    Akka, Kafka, Spark
    Spring, OSGi, Camel
    Vert.x, Spring Reactor
    Hibernate, ATG, Rails
    Drupal, Django
    \section{databases}
    PostgreSQL, MySQL
    MariaDB, Oracle
    Cassandra, Hive
    Elasticsearch
    SQL Server, MongoDB
    \section{tools}
    Git, Subversion, CVS
    Bazaar, Mercurial
    Gradle, Maven, Ant
    SBT, Make, Docker
    Mesos, Marathon
    Jenkins, Bamboo, JIRA
    GitHub, Bit Bucket
    \section{servers}
    Karaf, Tomcat, Jetty
    Apache, WebLogic
    ActiveMQ, ZeroMQ
    \section{os}
    GNU/Linux, macOS
    \section{interests}
    functional programming
    mathematics
    machine learning
    microservices
    devops
    modularity
    fast data
\end{aside}

\section{abstract}
A senior software engineer and craftsman working on fast data and big data
applications with a focus on functional programming, reactive streams,
reactive microservices, architecture, devops, and development.
Loves learning about and evangelizing new technology and refining existing
tech. Expert in Scala and Java, and experienced or familiar with several
other languages and platforms. PMC Chair of the Apache Logging Services
project, member and VP of the Apache Software Foundation, contributor to several
open source projects outside the ASF, board member of the Illinois Java
User Group, technical blogger, and speaker at conferences and meetup
groups. Long time advocate of free/libre and open source software.

\section{history}

\begin{entrylist}
    \entry{Dec 2017--\\Now}{Consulting Senior Software Engineer}{Spantree Technology Group, Chicago, IL}{
        Senior software engineer independently consulting with Spantree Technology Group
        in Chicago. Projects and responsibilities include:
        \begin{itemize}
            \item Developed a fake data generator for benchmarking various Elasticsearch
                mapping and indexing scenarios using RxKotlin.
            \item Developed a query load tester for Elasticsearch using the Gatling framework.
            \item Collaborated with principle engineer to write statements of work.
        \end{itemize}
    }
\end{entrylist}
\begin{entrylist}
    \entry{Nov 2016--\\Nov 2017}{Senior Consultant}{SPR Consulting, Chicago, IL}{
        Senior software engineer and architect at Uptake Technologies in Chicago
        where projects and responsibilities included:
        \begin{itemize}
            \item Developed a plugin for Apache Kafka Connect to consume Apache
                Avro-encoded Kafka messages, produce Apache Parquet-encoded files,
                and upload them to Amazon S3 for use in Amazon Elastic MapReduce.
            \item Developed a Kafka Streams application to monitor and automatically
                fix broken Kafka Connect tasks.
            \item Developed an Apache Spark process for synchronizing a gold and silver
                Apache HDFS data lake cluster along with Apache Hive metadata.
            \item Collaborated on a data sandbox interface for the above data lake using
                Apache Zeppelin, Apache Spark, Apache YARN, Amazon EMR, and other
                Apache Hadoop projects.
            \item Developed an enhancement to an in-house deployment manager to support
                Kafka Connect tasks.
            \item Wrote internal engineering blog posts and organized internal lunch and
                learns, and helped with Uptake University.
            \item Worked with the Open Source Committee as an open source community
                and project management consultant as well as contributing multiple projects
                to this including updates to Scalaz, a Log4j Slack plugin, and a Scala compiler
                patch to help detect incorrectly inferred types.
            \item Developed an Akka Streams application to query, stream, and export
                mass amounts of IoT signal data stored in Apache Cassandra to CSV and
                the REST API for a web UI for visualizing said data.
        \end{itemize}
    }
\end{entrylist}
\begin{entrylist}
    \entry{(Cont.)}{Senior Consultant}{SPR Consulting, Chicago, IL}{
        \begin{itemize}
            \item Developed a Vert.x microservice for managing user-uploaded media files
                in a cloud-agnostic fashion.
            \item Developed an Elasticsearch connection pooling library to help with
                connectivity issues.
            \item Developed an integration service in Spring Boot and Reactor for a
                REST API used for a wind turbine monitoring dashboard along with other
                production-hardening features like service discovery, client side load
                balancing, failover, etc., along with Maven to Gradle conversions and
                migration to using Jenkins pipelines.
        \end{itemize}
        At SPR Consulting, I also did part time developer evangelism via technical
        blogging and speaking at conferences and meetups. Topics include:
        \begin{itemize}
            \item Logging from both a developer's and operator's perspective
                (both blog and talk at Chicago Java User Group, 9 Nov 2017).
            \item Scala for Java developers (talk at Illinois Java User Group, 11 July 2017).
            \item Using Akka and Scala to implement event sourcing and CQRS.
            \item Why use a microservices architecture.
            \item A proposal on reactive microservice security similar to federation.
            \item Spring 5, Reactor, and reactive streams.
            \item The Lagom framework for reactive microservices.
            \item Use of Apache Avro, Thrift, and alternatives to typical REST/JSON
                architectures (talk at Mulesoft Connect 2017).
        \end{itemize}
        All listed blog items are available on my blog at \url{http://musigma.org/} along
        with mirrors on \url{http://spr.com/}.
    }
\end{entrylist}
\begin{entrylist}
    \entry{2014--Now}{VP, Apache Logging Services}{Apache Software Foundation}{
        Project Management Committee member of the Apache Logging Services project
        and Member of the Apache Software Foundation.
        Serving as the PMC Chair (VP) since October 2017. Performs development,
        support, documentation, and release management for projects including
        Log4j 2, Log4j Scala API, and Chainsaw. Highlights:
        \begin{itemize}
            \item Significant updates to the plugin system to make plugins easier
                and less tedious to write.
            \item Streamlining property-based configuration and other config APIs.
            \item Additional logging system bridges and APIs to make other future
                logging libraries easier to integrate with.
            \item Automated test overhauls and documentation updates.
            \item Additional plugins including an Apache Cassandra appender.
            \item Release manager for Log4j2, Log4j Scala API, Logging Parent, and Chainsaw.
            \item Presented at ApacheCon Denver 2014: Intro to Log4j 2.0.
            \item Presented at CJUG: The How and Why of Logging (9 Nov 2017).
        \end{itemize}
        I am also a committer on the Apache Commons project which is a collection
        of various low-level libraries for use in any Java application including
        projects such as Apache Commons Pool and Apache Commons DBCP.
        Other presentations I've done related to Apache include:
        \begin{itemize}
            \item Presented at IJUG: Event Driven Architecture Using Apache Kafka (17 Jan 2018).
            \item Use of Apache Avro, Thrift, and alternatives to typical REST/JSON
                architectures (panel at Mulesoft Connect 2017).
        \end{itemize}        
    }
\end{entrylist}
\begin{entrylist}
    \entry{2013--2014,\\2015--\\Nov 2016}{Senior Software Engineer}{Peapod, Chicago, IL}{
        Member of the Webcenter division in Peapod responsible for the development and
        maintenance of our sister grocery store websites (Stop \& Shop, Giant Foods,
        and Martin's Foods). Highlights:
        \begin{itemize}
            \item Collaborated with project managers, QA testers, web developers,
                database administrators, system administrators, and other engineers
                to make a content management system integrated with various loyalty,
                coupon, and user account systems.
            \item Developed a modular, reactive, REST-driven integration API using
                Apache Camel, Karaf, ActiveMQ, Netty, Hazelcast, Spark, Hibernate,
                and various other supporting libraries.
            \item Developed a Spring MVC proxy application around our ESB to allow
                OAuth2-protected REST APIs to be used by our websites and mobile apps.
            \item Administered CentOS VMs that host these applications.
            \item Developed build and deployment infrastructure using Atlassian
                Bamboo and Docker.
            \item Developed a CMS using Oracle Commerce (ATG) on WebLogic.
        \end{itemize}
    }
\end{entrylist}
\begin{entrylist}
    \entry{2011--2013}{Principle Engineer}{Deep Dish Development, Mount Prospect, IL}{
        As one of two co-founders, I administered the business, servers, databases,
        finances, and other fine details of launching and maintaining a small web
        development consultancy. Highlights:
        \begin{itemize}
            \item Set up and maintained multiple GNU/Linux server environments on
                AWS running Apache, MySQL, PHP, Ruby, and Java.
            \item Helped form a business plan and company structure.
            \item Contributed general programming knowledge, training, and mentoring.
            \item Managed the company's finances and billing.
        \end{itemize}
    }
\end{entrylist}
\begin{entrylist}
    \entry{2011}{Lead Programmer}{LRH Advertising, Glenview, IL}{
        Full stack web developer for a retirement portal using Drupal and
        PHP. Highlights:
        \begin{itemize}
            \item Migrated server platform to AWS using EC2, S3, RDS, and Route53.
            \item Developed a prototype social networking site for retirees.
            \item Administered an Apache web server and MySQL database.
            \item Introduce the use of Git for version control of the software.
        \end{itemize}
    }
\end{entrylist}
\begin{entrylist}
    \entry{2011}{Full Stack Developer/SEO Consultant}{Lights America, Wheeling, IL}{
        Search engine optimization consultant and general full stack web
        developer. Here I helped optimize a large network of lighting
        showroom websites to all load much faster. Highlights:
        \begin{itemize}
            \item Migrated image hosting infrastructure to Amazon S3 and CloudFront.
            \item Modernized legacy HTML sites into clean, standards compliant
                HTML, CSS, and JavaScript.
            \item Referred and trained a full time web developer to take over
                maintenance of the existing sites.
        \end{itemize}
    }
\end{entrylist}

\section{education}
\begin{entrylist}
    \entry{2010--2012}{Studied Mathematics, Computer Science}{Roosevelt University, Chicago, IL}{
        Dual focus in mathematics and computer science with a focus on pure math
        and machine learning.
    }
    \entry{2007--2009}{}{Oakton Community College, Des Plaines, IL}{
        Completed many core requirements and undergrad classes for mathematics
        and computer science.
    }
\end{entrylist}
\end{document}
